Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/introduction.tex
as I have suspected, the only previous model I need to introduce is the AG model.
This commit changes the introductions of several chapters and lowers the headings by one in the new AG model chapter
tweaks and dedication

In this thesis, I will present an extension of the work of Michalik and Sipe~\cite{michalik_analytic_2006,michalik_erratum:_2008}, describing electron bunch propagation in an mean-field self-similar Analytic Gaussian (AG) pulse treatment, to include the influence of linear external forces due to electron optical elements.
The resulting computationally efficient propagation analysis can then be used to model, and hence design, UEM columns and UED systems in a straightforward manner.
For completeness, in Section \ref{sec:ms_model} I will introduce, in MKS units, the essential features of the AG model.
In Chapter \ref{chap:extension}, I present some optimizations to the AG model, and develop useful initial conditions representing single-photon photoemission from a typical metal photocathode.
I then present my extensions to the Michalik and Sipe AG model which permit the inclusion of generic external forces.
In order to adapt this extended AG model for simulating pulses in a realistic UEM column, I then present specific contributions that arise from magnetic lenses, RF cavities and DC accelerators.
I would like to note that the analyses presented are performed in the non-relativistic limit, which is a reasonable approximation for the typical 20-200keV electron energies employed in UED and electron microscopy.

@@

In Chapter \ref{chap:model_results}, I apply the AG model to draw some initial insight into the behaviors of ultrafast electron pulses in a UEM column.
Then in Chapter \ref{chap:considerations}, I apply some well known results from the field of electron microcopy, namely the Rose criterion~\cite{rose_television_1948}, an ultrafast analog to the Child-Langmuir law~\cite{child_discharge_1911,langmuir_effect_1923,valfells_effects_2002}, and the conservation of transverse emittance~\cite{jensen_emittance_2010} (each of which will be introduced) to arrive at two design goals for building a UEM which will produce high-resolution images.
First, that the electron pulses should be emitted from a large-area source, and second, that every effort must be made to reduce the initial rms transverse momentum (i.e., the emission cone angle).

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype} I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
The, before I conclude, in \ref{chap:photocathode}, I highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum.
I will present several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work may even challenge our current understanding of photoemission.

>>>>

In this thesis, I will present an extension of the work of Michalik and Sipe~\cite{michalik_analytic_2006,michalik_erratum:_2008}, describing electron bunch propagation in an mean-field self-similar Analytic Gaussian (AG) pulse treatment, to include the influence of linear external forces due to electron optical elements.
The resulting computationally efficient propagation analysis can then be used to model, and hence design, UEM columns and UED systems in a straightforward manner.
For completeness, in Chapter \ref{chap:ms_model} I will introduce, in MKS units, the essential features of the AG model.
In Chapter \ref{chap:extension}, I present some optimizations to the AG model, and develop useful initial conditions representing single-photon photoemission from a typical metal photocathode.
I then present my extensions to the Michalik and Sipe AG model which permit the inclusion of generic external forces.
In order to adapt this extended AG model for simulating pulses in a realistic UEM column, I then present specific contributions that arise from magnetic lenses, RF cavities and DC accelerators.
I would like to note that the analyses presented are performed in the non-relativistic limit, which is a reasonable approximation for the typical 20-200keV electron energies employed in UED and electron microscopy.

@@

In Chapter \ref{chap:model_results}, I apply the AG model to draw some initial insight into the dynamics of ultrafast electron pulses traversing a UEM column.
One of the conclusions that I will draw is that oblate, or ``disk-like'', electron pulses will be generally preferred to prolate ``cigar-like;'' for UEM, the electron pulses are likely to be oblate for reasonably sized incident laser spot sizes.
Then in Chapter \ref{chap:considerations}, I apply some well known results from the field of electron microcopy, namely the Rose criterion~\cite{rose_television_1948}, an ultrafast analog to the Child-Langmuir law~\cite{child_discharge_1911,langmuir_effect_1923,valfells_effects_2002}, and the conservation of transverse emittance~\cite{jensen_emittance_2010} (each of which will be introduced) to arrive at two design goals for building a UEM which will produce high-resolution images.
First, that the electron pulses should be emitted from a large-area source, and second, that every effort must be made to reduce the initial rms transverse momentum (i.e., the emission cone angle).

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype}, I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
Then, before I conclude, I will in Chapter \ref{chap:photocathode} highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum.
I will present several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work may even challenge our current understanding of photoemission.
